### 2024-06-24 basic-statistics.qmd
20240624 - align formulas

$$
df_\text{between} = g - 1
df_\text{within} = N - g
$$ {#eq-dfOneWayANOVA}

@@

$$
df_\text{Factor A} = a - 1
df_\text{Factor B} = b - 1
df_\text{Interaction} = (a - 1)(b - 1)
df_\text{error} = a * b * (N - 1)
$$ {#eq-dfFactorialANOVA}

@@

$$
df_1 = T - 1
df_2 = (T - 1)(N - 1)
$$ {#eq-dfRepeatedMeasuresANOVA}

where $N$ is sample size and $T$ is the number of timepoints.

@@

$$
df_1 = p
df_2 = N - p - 1
$$ {#eq-dfMultipleRegression}

>>>>

$$
\begin{aligned}
  df_\text{between} &= g - 1 \\
  df_\text{within} &= N - g
\end{aligned}
$$ {#eq-dfOneWayANOVA}

@@

$$
\begin{aligned}
  df_\text{Factor A} &= a - 1 \\
  df_\text{Factor B} &= b - 1 \\
  df_\text{Interaction} &= (a - 1)(b - 1) \\
  df_\text{error} &= ab(N - 1)
\end{aligned}
$$ {#eq-dfFactorialANOVA}

@@

$$
\begin{aligned}
  df_1 &= T - 1 \\
  df_2 &= (T - 1)(N - 1)
\end{aligned}
$$ {#eq-dfRepeatedMeasuresANOVA}

where $N$ is sample size and $T$ is the number of timepoints (or conditions).

@@

$$
\begin{aligned}
  df_1 &= p \\
  df_2 &= N - p - 1
\end{aligned}
$$ {#eq-dfMultipleRegression}
